---
title: "Data Wrangling I: Data Import"
output: html_document
---
```{r}
library("tidyverse")
```

## Data Paths
Let's import the `FAS_litters.csv`
```{r}
litters_df=read_csv("./data/FAS_litters.csv")
```

use `janitor::clean_names()` to clean up variable names after importing data. Doing so will take whatever the column names are and convert them to lower snake case.
```{r}
names(litters_df)
#make the variable names all lowercase
litters_df=janitor::clean_names(litters_df)
names(litters_df)
```

_**Learning Assessment: **_load the FAS_pups.csv dataset
```{r}
pup_df=read_csv("./data/FAS_pups.csv")
litters_df=janitor::clean_names(litters_df)
```
## Looking at data
```{r}
litters_df
head(litters_df)
tail(litters_df)
```
You can use `view(litters_df)` to view the whole dataset.

Looking at a data summary
```{r}
str(litters_df)
```
Another tool is `skimr::skim`, although it’s more “neat” than useful.
```{r}
skimr::skim(litters_df)
```

## Options in `read_*`

* `col_names`: usually TRUE. If FALSE, column names are X1, X1, … . You can also supply column names.
* `na`: string vector containing character expressions for missing values.
* `skip`: number of rows to skip before reading data.

Skip the first 10 rows, and not assume the first row are variable names
```{r}
litters_df=read_csv("data/FAS_litters.csv",skip=10,col_names=FALSE)
```

Look at NA values

The following code can replace all the number 19 in the dataset with `NA`
```{r}
litters_df=read_csv("data/FAS_litters.csv",na=c("NA",19))
```

